\documentclass{acm_proc_article-sp}

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
%\usepackage{natbib}
\DeclareCaptionType{copyrightbox}

\usepackage{tikz}
\usetikzlibrary{backgrounds, fit, shapes}

\usepackage{hyperref}
\hypersetup
{
	colorlinks=true,
}

\makeatletter
\let\@copyrightspace\relax
\makeatother

\begin{document}

\title{The Code Following: Why do coders follow a project?}
\numberofauthors{2}
\author{
\alignauthor
Jose Calvo-Villagran\email{jcalvovi@uwaterloo.ca}
\and
\alignauthor
Madhur Kukreti\email{mkukreti@uwaterloo.ca}
}

\maketitle

\begin{abstract}
Code  repositories  are  collaborative  environments  for  software development. Their usage has now become widespread, being github one of the most popular ones (over 3.5 million users and ten million repositories). This is especially true for open source projects, in which the usage of public  code  repositories has become some sort  of  standard.  The  advantages of  using  such systems  are  numerous, from version control and issue tracking to getting involved  in  a community of developers and share communication tools. The large amount of projects that a developer can join and contribute seems overwhelming. Yet, somehow,  some  of  the  projects  seem  to  be  more  attractive  to  developers  and  have  larger communities  that  are  willing  to  contribute  to  their  development.  A  simple  intuition  of  this phenomenon would be that popular projects attract developers simply because they are popular, like a snowball effect. While this might be true for some projects, various counterexamples can be found in which  a project quickly gathers a significant following, with no obvious reason. Our study will focus on analyzing the social network of public code repositories. Hopefully, by the end of our study we will provide some answers to the following questions:

\textbf{Q1:} Why do people follow a project?

\textbf{Q2:} What is a typical follower of a project?

We believe that by answering these questions we can help developers build a following to their projects. We will work on Github. It is one of the most widely used public code repositories and it includes several  social  network  features, like the ability of a developer  to  follow  projects  and  other developers.  Github  is  also  suitable for our project  because it allows public access to user's profiles.
\end{abstract}

% A category with the (minimum) three required fields
\category{K.4.3}{Organizational Impacts}{Computer-supported collaborative work}
%A category including the fourth, optional field follows...
\category{D.2.9}{Management}{Programming Teams}

\terms{Human Factors, Contributors, Open Source}

\keywords{Repositories, Social Networking, Software Engineering} % NOT required for Proceedings

\input{./tex/intro.tex}
\input{./tex/related_work.tex}
\input{./tex/data_collection.tex}
\input{./tex/results.tex}
\input{./tex/threats-to-validity.tex}
\input{./tex/conclusions.tex}

\bibliographystyle{plain}
\bibliography{paper}
\end{document}
